---
title: "writing_functions"
author: "Felix Tran"
date: "October 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
```

# Writing our first function

Start small
```{r}
set.seed(1)
x <- rnorm(25, 5, 3)
(x - mean(x)) / sd(x)

z_scores <- function(x) {
  (x - mean(x)) / sd(x)
}

y <- runif(100)
z_scores(y)
```

Putting in checks on inputs help make your functions break less often
```{r}
z_scores <- function(x) {
  if (!is.numeric(x))
    stop("Argument x should be numeric")
  else if (length(x) == 1)
    stop("Z scores cannot be computed for length 1 vectors")
  
  z <- mean(x) / sd(x)
  z
}

# z_scores("hi")
# z_scores("iris")
# z_scores(1)
```

# Making larger functions
```{r}
mean_and_sd <- function(x) {
  if (!is.numeric(x))
    stop("Argument x should be numeric")
  else if (length(x) == 1)
    stop("Z scores cannot be computed for length 1 vectors")
  
  tibble(
    mean_x = mean(x),
    sd_x = sd(x)
  )
}

mean_and_sd(y)
```

# Multiple inputs
Now we look at single linear regression. We can write a function that simulates
data and fits the model as a simple linear regression.
```{r}
sim_data = tibble(
  x = rnorm(30, 1, 1),
  y = 2 + 3*x + rnorm(30, 0, 1)
)

ggplot(sim_data, aes(x = x, y = y)) +
  geom_point()

ls_fit <- lm(y ~ x, data = sim_data)
beta0_hat <- coef(ls_fit)[1]
beta1_hat <- coef(ls_fit)[2]

sim_regression <- function(n, beta0, beta1) {
  sim_data = tibble(
    x = rnorm(n, 1, 1),
    y = beta0 + beta1*x + rnorm(n, 0, 1)
  )

  ls_fit <- lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat <- coef(ls_fit)[1],
    beta1_hat <- coef(ls_fit)[2]
  )
}

sim_regression(50, 0, 1)
```

# Revisiting old examples
Functions make certain tasks much easier. You can iterate the same action
a bunch of times without retyping it every iteration.
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

```{r}
extract_reviews <- function(url) {
  dynamite_html = read_html(url)

  review_titles = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = dynamite_html %>%
      html_nodes(".review-data:nth-child(4)") %>%
      html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
}

extract_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")
```

We can iterate the function over multiple pages
```{r}
url_base <- "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls <- str_c(url_base, 1:5)

dynamite_reviews <- bind_rows(
  extract_reviews(urls[1]),
  extract_reviews(urls[2]),
  extract_reviews(urls[3]),
  extract_reviews(urls[4]),
  extract_reviews(urls[5])
)

dynamite_reviews
```

Writing a function for an old Lord of the Rings sample
```{r}
lotr_reading <- function(range, name) {
  movie <- readxl::read_excel("./Data/LotR_Words.xlsx", range = range) %>% 
    mutate(movie = name)
  
  movie
}

lotr_tidy <- 
  bind_rows(lotr_reading("B3:D6", "fellowship_ring"),
            lotr_reading("F3:H6", "two_towers"),
            lotr_reading("J3:L6", "return_king")) %>% 
  janitor::clean_names() %>% 
  gather(key = sex, value = words, female:male) %>% 
  mutate(race = tolower(race)) %>% 
  select(movie, everything())

lotr_tidy

```

# Final thoughts
You can use functions as arguments to other functions